### 2010-02-17 trunk/deliverables/D5_2_2/fast_d5_2_2.tex
minor changes
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@566 d8b0c59b-6544-0410-94d9-83a5658a058e

\clearpage
\section{Introduction} % (fold)
\label{sec:introduction}
This section starts establishing the goal and scope of the present deliverable, and shows references to other deliverables for further information.

\subsection{Goal and Scope} % (fold)
\label{sub:goal_and_scope}

The semantic catalogue will store and index screen-flow resources and back-end Web services, locate appropriate Web services for users, endow gadgets with functionality based on Service descriptions and resolve mediation problems between gadgets and their back-end services.

This document serves as an appendix to the semantic catalogue deliverable.

% subsection goal_and_scope (end)

\subsection{Changes from previous version} % (fold)
\label{sub:changes_from_previous_version}

This document is not intended to provide any further information regarding the semantic catalogue prototype. For information regarding where the code of the catalogue can be found, installation instructions, system requirements, a overview of the catalogue architecture and a detail API, please read \cite{palaguita2010_usermanual}.

>>>>

\clearpage
\section{Introduction} % (fold)
\label{sec:introduction}

Because D5.2 is a pure software deliverable, the sole role of this document is to function as a starting point for further information about the catalogue. Nevertheless, the deliverable D5.1 is aimed to fulfil this purpose, so for any further information such as where the code of the catalogue can be found, installation instructions, system requirements, a overview of the catalogue architecture or a detailed API, please read \cite{palaguita2010_usermanual}.
